Classical Mechanics Assignment 9

### 2015-12-02 classical/latex/a9.tex
Add working crystal movie generation.

\section{Problem One: }

>>>>

\section{Problem One: Inertia tensor of 4-particle system}

\textbf{A four particles system consists of masses $m_i$ at coordinates:}
\begin{align*}
  m_1 &= 5m\\
  \vec{r_1} &= (a, 2a, 0)\\
  m_2 &= 5m\\
  \vec{r_2} &= (0, -2a, a)\\
  m_3 &= 5m\\
  \vec{r_3} &= (a, a, -a)\\
  m_4 &= 5m\\
  \vec{r_4} &= (3a, a, -2a)\\
\end{align*}
\textbf{Find the inertia tensor, the principal axes, and the moments of inertia. Explicitly check that the principal axes are orthogonal to each other. (Hint: you can use an online solver for the third degree polynomial, such as: http://www.calculatorsoup.com/calculators/algebra/cubicequation.php)}
